### 2023-12-07 thesis/chapters/03-design.tex
BVS inspection and data

\section{Research questions}
Main goals:
	- How does vibration data look like (spectral and time domain)?
	- Create dataset of machinery vibrations
	- Reduce number of features (samples) send from edge device - to minimal amount
	- Adapt to features changing over time (RiverML can handle it, find proof)
	- Evaluate model performance on all features and different feature sets
	- Keep in mind: data ordering!

\section{Data preparation}
- Mafaulda dataset
	- Choose 4 faults - normal (N), imbalance (I), vertical (VM) and horizonal misalignment (HM)
	- Convert severity to 0 - 1 scale.
		- Label samples above 0.5, 0.7, 0.9 as anomalous
	- Choose rpm range 2900 $\pm$ 500 (around rotational speed of machinery with some spread, some features are correlated with rpm 
	- Counts before split: 
		- Split to 5 parts of 1 second intervals
	- Two measurement points A, B
	- Detrending by removing mean
	- Calculate features: temporal, spectral (in 5 window sizes): welch averaging, hann window

@@

\section{Feature relevance}
- choose 3 features
- supervised
	- highly correlated features >= 0.9:
		- Temporal domain (A)
			- std, rms, 1.000000
			- margin, impulse, 0.999079
			- crest, impulse, 0.996807
			- crest, margin,	0.992548
			- pp, max, 0.970055
			- max, (std, rms), 0.938198
			- pp, (std, rms), 0.938180 / 0.928
		- Spectral domain (A)
			- same feature in different window sizes (0.99)
			- kurtosis, skewness, 0.980618
			- std, energy, 0.960110
			- entropy, noisiness, 0.945514

	- calcultate euclidian measure of feature 
	- correlation point biserial, fisher, mutual information
		- Sperman rank correlation: corr, f_stat, 1.000000
	- calculate feature rank
		- Temporal (A) - Remove corr: pp, skewness, margin
			pp	1.442250
			std	2.080084
			max	2.714418
			rms	3.174802
			skewness	6.082202
			margin	6.868285

			(B)			
			skewness	1.817121
			rms	1.817121
			std	2.289428
			kurtosis	4.308869
		- Spectral (A) - multiple window sizes 
			- (energy, roll off, std)

@@

\section{Nearest neighbour classifier}
- kNN (fault and anomaly)
	- Offine (baseline)
	- Online (evolution)
- parameters: k-neigh, distance
- metrics: accuracy, precision, recall

>>>>

\section{Research questions}
Open ended Research questions:
	- Which time and frequency features can be extracted from vibrational signals to provide an accurate record of machinery faults?
	- What are the savings in transmission bandwidth when chosen signal features are used in comparison to raw sampled measurement or lossless compression techniques?
	- How can the machinery faults be continuously identified based on collected events?

Main goals:
	- How does vibration data look like (spectral and time domain)?
	- Create dataset of machinery vibrations
	- Reduce number of features (samples) send from edge device - to minimal amount
	- Adapt to features changing over time (RiverML can handle it, find proof)
	- Evaluate model performance on all features and different feature sets
	- Keep in mind: data ordering!

\section{Data preparation}
- Machinery:
   - KALORIK BASIC Stand Fan TKGVT1037C  - height 125 cm, stable 60 cm cross base, 3 speed, 45 W, 45 cm fan diameter, 3 propelers
   - AC unit VERTIV: Scroll Compressor: Copeland ZR16M3E-TWD-561 (2900 RPM @ 50 Hz; 9.7 kW (13 HP); 380/420V; 25 A) - 2 units
   - Water pump: KSB Omega 300-560 B GB G F (2018, 1493 (1500) RPM @ 50 Hz; 500 kW elektromotor; power requirement: 380 kW) - 1 unit

- Sensors:
	- Accelerometer: ADXL335 ($\pm$3g, Bandwidth: 0.55 kHz)
	- Noise density: 150 - 300 $\mu g / \sqrt{Hz}$ rms
	- Resolution: 12 bits
	- Axis: 3 axis
	- Sensitvity: 300 mV/g
	- Sample time: 400 ns (2.5 kHz)
	- Voltage range: up to 1.8 V

	- IIS3DWB (STEVAL-MKI208V1K) Digitálny (SPI), 1 / 3 axis, Resultution: 16 bits ADC, Range: 2 - 16g, Sensitvity: 0.061 mg/LSB pri 2g, Noise density:: 75 $\mu g / \sqrt{Hz}$, ODR: 26.7 kHz,Bandwidth: 5 - 6.3 kHz (-3 dB), FIFO: 3 kB (512 vzoriek)

- EDA
	- Time waveform
	- Spectrogram
	- Features: boxplot

- Experiment subsets:
	features = temporal, spectral
	rpm_limit = False, True
	hardware = shaft, bearings
	target = fault, anomaly_60, anomaly_90
	placement = A, B
	online = False, True

- Mafaulda dataset
	- Choose 4 faults - normal (N), imbalance (I), vertical (VM) and horizonal misalignment (HM)
	- Convert severity to 0 - 1 scale.
		- Label samples above 0., 0.9 as anomalous
	- Choose rpm range 2900 $\pm$ 500 (around rotational speed of machinery with some spread, some features are correlated with rpm 
	- Counts before split: 
		- Split to 5 parts of 1 second intervals
	- Two measurement points A, B
	- Detrending by removing mean
	- Calculate features: temporal, spectral (in 5 window sizes): welch averaging, hann window

@@

- \textbf{Measurements-SHC3.html}
- \textbf{BVS-Measurements.html}

\section{Feature relevance}
- \textbf{FeatureSummary.html}

- choose 3 features
- supervised
	- highly correlated features >= 0.9:
		- Temporal domain (A)
			- std, rms, 1.000000
			- margin, impulse, 0.999079
			- crest, impulse, 0.996807
			- crest, margin,	0.992548
			- pp, max, 0.970055
			- max, (std, rms), 0.938198
			- pp, (std, rms), 0.938180 / 0.928
		- Spectral domain (A)
			- same feature in different window sizes (0.99)
			- kurtosis, skewness, 0.980618
			- std, energy, 0.960110
			- entropy, noisiness, 0.945514

	- calcultate euclidian measure of feature 
	- correlation point biserial, fisher, mutual information
		- Sperman rank correlation: corr, f\_stat, 0.98
	- calculate feature rank
		- Temporal (A) - Remove corr: pp, skewness, margin
		- Spectral (A) - multiple window sizes 
			- (energy, roll off, std)

@@

\section{Nearest neighbour classifier}
- \textbf{kNN.html}
- kNN (fault and anomaly)
	- Offine (baseline)
	- Online (evolution)
- parameters: k-neigh, distance
- metrics: accuracy, precision, recall
